A Minimal Book Example

### 2020-02-25 manuscript/drafts/manuscript.Rmd
update manuscript   - update notes   - update bookdown files

# path to all R folder
pathRdata <- "../../R/data/"
```

@@

Descriptive statistics on the five systematic reviews can be found in Table `r table_nums("datasets", display = "cite")`.

@@

@@

#### hall 
The review [@Hall2012], is reviewed in [@Yu2016].

@@

# Appendix A - list of definitions
Machine learning algorithms cannot predict the relevance of abstracts from the raw texts as they are. 
The content of the texts needs to be transformed into numerical representations. The processs of transforming texts to numerical feature vectors is called word embeddings.

>>>>

pathRdata <- "../../R/data/"

```

@@

Descriptive statistics on the five systematic reviews can be found in `r table_nums("datasets", display = "cite")`.

@@

Machine learning algorithms cannot predict the relevance of abstracts from the raw texts as they are. 
The content of the texts needs to be transformed into numerical representations. The processs of transforming texts to numerical feature vectors is called word embeddings.

####

@@

#### hall 
The review [@Hall2012], is reviewed in [@Yu2018a].

@@

# Appendix A - list of definitions

### 2020-02-25 manuscript/test/index.Rmd
update manuscript   - update notes   - update bookdown files

```{r include=FALSE}
# automatically create a bib database for R packages
knitr::write_bib(c(
  .packages(), 'bookdown', 'knitr', 'rmarkdown'
), 'packages.bib')
```

>>>>

```{r include=FALSE}
# automatically create a bib database for R packages
knitr::write_bib(c(
  .packages(), 'bookdown', 'knitr', 'rmarkdown'
), 'packages.bib')

# load all necessary packages
source("R/packages.R")

# path to all R folder
pathRdata <- "../../R/data/"

# set chunk default options knitr
knitr::opts_chunk$set(echo = FALSE)

```
